---
title: "Test API"
output: html_notebook
---

```{r setup}
# Packages ----
library(httr)
library(callr)
library(magrittr)
```

This notebook contains some simple ad-hoc tests and checks for verifying a
Plumber API.

## Start API
In order to test the API, it needs to be running. We can either start the API as
a background job within RStudio, or we can use the
[`callr`](https://callr.r-lib.org/) package to start a background API:
```{r}
plumber_api <- r_bg(function() {
  plumber::plumb(dir = ".")$run(swagger = TRUE, port = 5762)
})
```

```{r}
plumber_api$is_alive()
```

## Check API
Using the [`httr`](https://httr.r-lib.org/) package, we can send requests to the
API and investigate responses.

```{r}
base_url <- "http://localhost:5762"
```

```{r}
swagger_url <- paste0(rstudioapi::translateLocalUrl(base_url, absolute = TRUE), "/__swagger__/")
rstudioapi::viewer(swagger_url)
```

### echo
Send request
```{r}
r <- GET(base_url, path = "echo", query = list(msg = "Hi there!"))
```

Check status code
```{r}
status_code(r)
```

Check contents
```{r}
content(r, as = "text", encoding = "UTF-8") %>% 
  jqr::jq() %T>%
  print() %>% 
  jsonlite::fromJSON()
```

### simple-plot
Send request
```{r}
r <- GET(base_url, path = "simple-plot")
```

Check status code
```{r}
status_code(r)
```

Check contents
```{r}
content(r, as = "raw") %>% 
  magick::image_read()
```

### plot
Send request
```{r}
r <- POST(base_url, 
          path = "plot",
          body = upload_file("../data/diamonds.json"),
          query = list(facet = "cut"))
```

Check status code
```{r}
status_code(r)
```

Check contents
```{r}
content(r, as = "raw") %>% 
  magick::image_read()
```

### sum
Send request
```{r}
r <- GET(base_url, path = "sum", query = list(x = 19, y = 7))
```

Check status code
```{r}
status_code(r)
```

Check contents
```{r}
content(r, as = "text", encoding = "UTF-8") %>% 
  jsonlite::fromJSON()
```

## Kill API

```{r}
plumber_api$kill()
```